The Effects of Racial Identity and Discrimination on Political Participation and Political Attitudes

### 2025-01-08 draft_finalreport.qmd

  # Create plot
  ggplot(plot_data, aes(y = name)) +
    geom_vline(xintercept = 1, linetype = "dashed", color = "red", size = 0.7) +
    geom_point(aes(x = or), size = 4, color = "blue") +
    geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0.3, color = "black") +
    theme_minimal() +
    theme(
      axis.text.y = element_text(size = 6, color = "black"),
      axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
      axis.title.x = element_text(size = 12, face = "bold"),
      axis.title.y = element_text(size = 12, face = "bold"),
      plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
      plot.margin = margin(1, 1, 1, 1, "cm"),
      panel.grid.major.y = element_line(color = "gray90"),
      panel.grid.minor.y = element_blank()
    ) +
    labs(
      title = "Significant Variables with Confidence Intervals",
      x = "Odds Ratio",
      y = "Variables"
    )
}

@@

# Create the plot
ggplot(significant_data, aes(x = `Odds Ratio`, y = Variable)) +
  geom_point(size = 4, color = "blue") +  # Add points for odds ratios
  geom_errorbarh(aes(xmin = `Lower Confidence Interval`, 
                     xmax = `Upper Confidence Interval`), 
                 height = 0.3, color = "black") +  # Add horizontal error bars
  geom_vline(xintercept = 1, linetype = "dashed", color = "red", size = 0.7) +  # Add a vertical reference line at Odds Ratio = 1
  labs(
    title = "Odds Ratio of Significant Variables",
    x = "Odds Ratio",
    y = "Variable"
  ) +
  theme_minimal() +  # Use a minimal theme for better aesthetics
  theme(
    axis.text.y = element_text(size = 6, color = "black"),  # Improve y-axis text readability
    axis.title.x = element_text(size = 12, face = "bold"),  # Highlight x-axis title
    axis.title.y = element_text(size = 12, face = "bold"),  # Highlight y-axis title
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),  # Center the title
    plot.margin = margin(1, 1, 1, 1, "cm"),  # Adjust margins
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),  # Reduce x-axis text size
    legend.text = element_text(size = 8),  # Reduce legend text size
    legend.title = element_text(size = 9)  # Reduce legend title size
  )

>>>>

  # Create plot
  ggplot(plot_data, aes(y = name)) +
    geom_vline(xintercept = 1, linetype = "dashed", color = "red", size = 0.7) +
    geom_point(aes(x = or), size = 4, color = "blue") +
    geom_errorbarh(aes(xmin = ci_lower, xmax = ci_upper), height = 0.3, color = "black") +
    theme_minimal() +
    theme(
      axis.text.y = element_text(size = 6, color = "black"),
      axis.text.x = element_text(angle = 45, hjust = 1, size = 8),
      axis.title.x = element_text(size = 12, face = "bold"),
      axis.title.y = element_text(size = 12, face = "bold"),
      plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
      plot.margin = margin(1, 1, 1, 1, "cm"),
      panel.grid.major.y = element_line(color = "gray90"),
      panel.grid.minor.y = element_blank()
    ) +
    labs(
      title = "Odds Ratios (Significant Variables)",
      x = "Odds Ratio",
      y = "Variables"
    )
}

@@

# Create the plot
ggplot(significant_data, aes(x = `Odds Ratio`, y = Variable)) +
  geom_point(size = 4, color = "blue") +  # Add points for odds ratios
  geom_errorbarh(aes(xmin = `Lower Confidence Interval`, 
                     xmax = `Upper Confidence Interval`), 
                 height = 0.3, color = "black") +  # Add horizontal error bars
  geom_vline(xintercept = 1, linetype = "dashed", color = "red", size = 0.7) +  # Add a vertical reference line at Odds Ratio = 1
  labs(
    title = "Odds Ratios (Significant Variables)",
    x = "Odds Ratio",
    y = "Variable"
  ) +
  theme_minimal() +  # Use a minimal theme for better aesthetics
  theme(
    axis.text.y = element_text(size = 6, color = "black"),  # Improve y-axis text readability
    axis.title.x = element_text(size = 12, face = "bold"),  # Highlight x-axis title
    axis.title.y = element_text(size = 12, face = "bold"),  # Highlight y-axis title
    plot.title = element_text(size = 14, face = "bold", hjust = 0.5),  # Center the title
    plot.margin = margin(1, 1, 1, 1, "cm"),  # Adjust margins
    axis.text.x = element_text(angle = 45, hjust = 1, size = 8),  # Reduce x-axis text size
    legend.text = element_text(size = 8),  # Reduce legend text size
    legend.title = element_text(size = 9)  # Reduce legend title size
  )
